Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-10-12 TACAS2018/paper.tex
Some refining of the intro

%\todo{reword paragraph?}
Using state of the art verifiers, we evaluate these models against
automatically synthesised controllers using CEGIS-based synsthesis that
incorporate the above mentioned artifacts in different models of
Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
that exploits different aspects of the problem at each stage.

>>>>

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.  We offer a multi-tiered approach
%% that exploits different aspects of the problem at each stage.
